### 2023-01-20 doc/src/DuoPLIC.tex
Numerous small improvements to the text
Remove obsolete footnote about PLIC specification
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

The Advanced PLIC of the previous chapter is not backward compatible
with the original {\RISCV} PLIC.%
\footnote{%
A proposed standard for the original PLIC is the document
\textit{{\RISCV} Platform-Level Interrupt Controller Specification},
available as of mid-2021 here:
\z{https://github.com/{\allowbreak}riscv/{\allowbreak}riscv-plic-spec}.
However, both free implementations of the PLIC and those of some major
{\RISCV} vendors such as SiFive have been observed to differ in small
but significant ways from this document and from each other.
Some important details of the original PLIC were better documented in
older versions of
\textit{The {\RISCV} Instruction Set Manual, Volume~II: Privileged
Architecture}, in a chapter titled
``Platform-Level Interrupt Controller (PLIC).''
That chapter has since been removed from more recent versions of
\textit{The {\RISCV} Instruction Set Manual}.%
}
To ease the transition of software from the original PLIC to the
APLIC, a {\RISCV} system may have a \emph{\mbox{Duo-PLIC\/}}
that software can configure to act as either form of PLIC.
A \mbox{Duo-PLIC} is an extension of an APLIC, having all the
usual memory-mapped interfaces of an APLIC, plus, at some other
memory addresses, the memory-mapped interface of an original {\RISCV}
PLIC too.
When the \mbox{Duo-PLIC} has \emph{compatibility mode} enabled,
interrupts from the \mbox{Duo-PLIC} to harts are controlled exclusively
by the original PLIC side of the \mbox{Duo-PLIC};
and when compatibility mode is disabled, interrupts to harts
are controlled exclusively by the APLIC side of the
\mbox{Duo-PLIC}.
A \mbox{Duo-PLIC} comes out of reset with compatibility mode enabled,
so older software with no knowledge of an APLIC can see the
\mbox{Duo-PLIC} as an original PLIC.

>>>>

The Advanced PLIC of the previous chapter is not backward compatible
with the original {\RISCV} PLIC.
To ease the transition of software from the original PLIC to the
APLIC, a {\RISCV} system may have a \emph{\mbox{Duo-PLIC\/}}
that software can configure to act as either form of PLIC.
A \mbox{Duo-PLIC} is an extension of an APLIC, having all the
usual memory-mapped interfaces of an APLIC, plus, at some other
memory addresses, the memory-mapped interface of an original {\RISCV}
PLIC too.
When the \mbox{Duo-PLIC} has \emph{compatibility mode} enabled,
interrupts from the \mbox{Duo-PLIC} to harts are controlled exclusively
by the original PLIC side of the \mbox{Duo-PLIC};
and when compatibility mode is disabled, interrupts to harts
are controlled exclusively by the APLIC side of the
\mbox{Duo-PLIC}.
A \mbox{Duo-PLIC} comes out of reset with compatibility mode enabled,
so older software with no knowledge of an APLIC can see the
\mbox{Duo-PLIC} as an original PLIC.
